---
title: "Assignment 1.5"
subtitle: "CPSC 292 Section ## (Instructor last name)"
author: "Your Name"
date: "09/06/2023"
output: html_notebook
---

## Assignment 1.5 -- Basic R Functions

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Command-line code that produces a search for the term “deviation” in all R help documents. How many entries are there?*

```{r}

```

### Question 2

*Assigns a value of 4.58e−7 to the letter a.*

```{r}

```

### Question 3

*Calculates the log of 2401 in base 7.*

```{r}

```

### Question 4

*Calculates the square root of 56.*

```{r}

```

### Question 5

*Calculates the mean of the following values: 7.33, 8.24, 8.88, 6.42, 3.51.*

```{r}

```


### Question 6

*One line of code which contains a deliberate syntax error. Explain what the error is in a comment below the line and how to fix it.*

```{r}

```

Turn in this RMD file.
