---
title: "Assignment 1.8"
subtitle: "CPSC 292 Section ## (Instructor last name)"
author: "Your Name"
date: "09/13/2023"
output: html_notebook
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.8 -- Matrices

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Create a 5 by 6 matrix of random numbers using `runif()` to generate data and store it in a variable named my.matrix1. (The function `runif()` pulls pseudorandom numbers from a normal distribution.)*

```{r}

```

### Question 2 

*Create another matrix using a different method with `runif()` to generate data that is 6 by 5 and store it in a variable named my.matrix2.*

```{r}

```

### Question 3

*Using a third method, create another matrix using `runif()` to generate data that is 5 by 10 and store it in a variable named my.matrix3.*

```{r}

```

### Question 4

*Use functions to find each of these values.* 

  a. *What are the dimensions of your three matrices?* 
  
```{r}

```

  b. *How many rows and columns do each have?* 
  
```{r}

```
  
  c. *How many numbers do each contain?*
  
```{r}

```

### Question 5

*What are the values at column 5 row 3 for each of your three matrices?*

```{r}

```

### Question 6

*The following line of code does not work. Correct the error so that my.matrix4 is a 5 by 16 matrix.*

```{r}
my.matrix4 <- cbin(my.matrix2, my.matrix3)
```

Turn in this RMD file.