---
title: "Assignment 1.6"
subtitle: "CPSC 292 Section ## (Instructor last name)"
author: "Your Name"
date: "09/08/2023"
output: html_notebook
---

## Assignment 1.6 -- Data Types in R

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*For the following inputs, list all of the data type(s) that would be appropriate to store data in R. Code the example for each.*

  a. *The word fart*
  
  Your answer here.
```{r}

```
  b. *The condition TRUE*
  
  Your answer here.
```{r}

```
  c. *The vector < FALSE, TRUE, FALSE, FALSE, TRUE >*
  
  Your answer here.
```{r}

```
  d. *The vector < 1, 0, 1, 0 >*
  
  Your answer here.
```{r}

```
  e. *The vector < 2.66, 2.66 >*
  
  Your answer here.
```{r}

```
  f. *The vector < 2i, 3+3i >*
  
  Your answer here.
```{r}

```
  g. *The number 8*
  
  Your answer here.
```{r}

```
  h. *The number 3.6*

  Your answer here.
```{r}

```

### Question 2

*For the following functions, what types of data do they accept as inputs and what data types do they return as outputs? Code a working example of each.*

 a. `median()`
  
  Your answer here.
```{r}

```

 b. `sd()`
 
  Your answer here.
```{r}

```
 
 c. `any()`
   
  Your answer here.
```{r}

```
 
 d. `cut()`
 
  Your answer here.
```{r}

```
 
 e. `order()`
  
  Your answer here.
```{r}

```

### Question 3

*Run the function `is.character()` on the coded example for each answer in question 1 (give each example
its own line). What does the output mean?*

```{r}

```

Your answer here. 

### Question 4

*Use the function `runif()` to produce 1000 random numbers between 0 and 1.*

```{r}

```

*How could you change the range from 10 to 1000 (instead of 0 to 1)? Write an explanation here describing the change and then put the adjusted code.*

Your answer here.

```{r}

```



Turn in this RMD file.
