---
title: "Lecture 1.6 Notebook"
author: "Lindsay Waldrop"
date: "9/11/2023"
output: html_notebook
---

## 1.6 Vectors

### Creating vectors in R

Creating vectors by assigning single values:
```{r}
v.scalar <- 3
```

Using the concatenate function `c()`:
```{r}
v.vector <- c(1, 2)
```

Check the length of a vector with the `length()` function:
```{r}
length(v.vector)
```

Make a vector with logicals: 
```{r}
v <- c(1L, 7L, 9L)
length(v)
```

What happens when you include a character data type?
```{r}
v2 <- c(1, "flower", 9)
```
R will coerce other types of data into characters if given character in an array or vector!

Making a sequence of numbers with `seq()` and `:`:
```{r}
vec <- seq(1, 10)
vec2 <- 1:10
vec3 <- seq(1, 10, 0.5)
vec4 <- seq(1, 10, length.out = 50)
```

Making a vector with repeating values using `rep()`: 
```{r}
repvec <- rep(1, 10)
vec1 <- c(1, 8, 10, 3)
repvec2 <- rep(vec1, times = 4)
repvec3 <- rep(vec1, times = 3, each = 2)
```

#### Check your understanding

Write one line of code to recreate this vector and store it as the object `boop`
1 1 1 2 2 2 3 3 3 4 4 4 5 5 5 1 1 1 2 2 2 3 3 3 4 4 4 5 5 5 1 1 1 2 2 2 3 3 3 4 4
4 5 5 5

```{r}

```

Write a *different* line of code that reproduces this vector and stores it as the object `boop2`:

```{r}

```

Test whether or not `boop` and `boop2` are the same using: 
```{r}
all.equal(boop, boop2)
```

### Getting info about vectors

Checking the length with `length()`:
```{r}
length(vec4)
```
Checking the data class with `class()`:
```{r}
class(vec4)
class(v2)
```

### Indexing specific values in vectors

Create a quick vector of even numbers between 2 and 20:
```{r}
blop <- seq(2, 20, by = 2)
```

Indexing each element is easy, just use square brackets `[ ]` and the position number of the value you want: 
```{r}
blop[1] # indexes the first element of blop
blop[4]
```

You can pull several elements by listing the positions you want: 
```{r}
blop[6:9]
blop[c(5, 7, 10)]
blop[c(4, 6, 8)]
```

You can even remove a value by adding a negative sign `-` in front of the position, this will remove that value from the vector: 
```{r}
blop[-3]
```

### Vectorized calculations

Calculations are vectorized in R, meaning that an operation on a vector acts on each element of a vector:
```{r}
blop*3
blop+3
blop - c(1, 2)
```


### Special Functions to vectors

These special functions act on all elements of the vector to produce one value: 
```{r}
sum(blop) # sum all the elements in a vector
prod(blop) # multiply the elements of a vector
mean(blop) # calculates the mean across elements of vector
sd(blop) # calculates standard deviation of elements of vector
```

#### Check Your understanding

The vector `blippi` has 12 elements:
```{r}
blippi <- c(2, 8, 9, 19, 39, 1, 9, 3, 48, 10, 23, 87)
```

What is the correct way to positions 3, 7, and 12 in a single line of code?
```{r}

```

Explain why the other suggested ways don't work: 

